25 years of Social Work Research

### 2015-03-24 dataCleaning.Rmd
Maps up and running

```{r initialization}
rm(list=ls())  
load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/SocialWorkHistory.Rdata")

# Load required packages
library(ggplot2)
library(dplyr)
library(gridExtra)
```

```{r eval=FALSE}
# Read data files
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
#countries.csv<-read.csv("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/countries.csv")

@@

@@

Insert Western Hemisphere Map Here

\newpage
Insert Eastern Hemisphere Map Here
\newpage
```{r}
plot.location.withUS
```

>>>>

```{r initialization}
rm(list=ls())  
#load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/socialWorkHistory.Rdata")

# Load required packages
library(ggplot2)
library(dplyr)
library(gridExtra)
library(rworldmap)

```{r eval=FALSE}
# Read data files
#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
#load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
#hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
#countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
countries.csv<-read.csv("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/countries.csv")

@@

```{r worldmap, eval=FALSE}

###Code for creating world maps.  The four countries in the UK are recoded as "United Kingdom" for data visualization.
library(rworldmap)

loc.tab<-table(locations$record)

loc.tab<-as.data.frame(loc.tab)
loc.tab<-select(loc.tab, country=Var1, frequency=Freq)

#join to a coarse resolution map
spdf <- joinCountryData2Map(loc.tab, joinCode="NAME", nameJoinColumn="country")

loc.tab2<-filter(loc.tab, frequency>=25)
spdf2 <- joinCountryData2Map(loc.tab2, joinCode="NAME", nameJoinColumn="country")

@@

```{r}
mapCountryData(spdf, nameColumnToPlot="frequency", catMethod="quantiles", 
                                  colourPalette="white2Black", 
                                  mapTitle="Article Countss by Country, 1989-2013")
```

\newpage
```{r}
mapCountryData(spdf2, nameColumnToPlot="frequency", catMethod="quantiles", 
                    colourPalette="white2Black", 
                    mapTitle="Article Counts for Countries with Sustained Presence, 1989-2013")

\newpage
```{r}
plot.location.withUS
```
